Bandit Multiclass Linear Classification: \\ Efficient Algorithms for the Separable Case

### 2019-05-08 ICML-camera-ready/np-hardness-of-the-weak-labeling-problem.tex
entomological changes; reviews; some formatting issues fixed
Fixes

We use symbols $1,2,\dots,K$ for strong labels and symbols $\overline{1},
\overline{2}, \dots, \overline{K}$ for weak labels. Formally, the weak
labeling problem can be described as below:
\begin{figure}[H]
\begin{framed}
\begin{center}
    \textbf{Weak Labeling}
\end{center}
\textbf{Given:} Feature-label pairs $(x_1, y_1)$, $(x_2, y_2)$, \dots, $(x_T, y_T)$ in $\{0,1\}^d \times \{1,2,\dots, K, \overline{1}, \overline{2}, \dots, \overline{K}\}$. \\
\textbf{Question:} Do there exist $ w_1, w_2, \dots, w_K \in \R^d$ such that for all $t=1,2,\dots,T$,
\begin{align*}
& y_t \in \{1,2,\dots,K\} \Longrightarrow \forall i \in \{1,2,\dots,K\} \setminus \{y_t\} \quad \ip{w_{y_t}}{x_t}  > \ip{w_i}{x_t} \; , \\
& \text{and} \\
& y_t \in \{\overline{1}, \overline{2},\dots, \overline{K}\} \Longrightarrow \exists i \in \{1,2,\dots,K\} \quad \ip{w_i}{x_t} > \ip{w_{\overline{y_t}}}{x_t} \; ?
\end{align*}
\end{framed}
\end{figure}

@@

We create the weak labeling instance as follows. Let $d=N+1$ and $K=3$.
Define $\zero$ as the zero vector $(0,\dots,0)\in \R^N$ and $\e_i$ as the
$i$-th standard vector $(0,\dots, 1, \dots, 0)\in \R^N$). Then we include all
the following feature-label pairs:
\begin{itemize}
\item Type 1: $(x,y)=((\zero,1), 3)$,
\item Type 2: $(x,y)=((\e_i,1), \overline{3})$ for all $i \in \{1,2,\dots,N\}$,
\item Type 3: $(x,y)=\left(\left(\sum_{i\in c_j} \e_i, 1\right), 3\right)$ for all $j \in \{1,2,\dots,M\}$.
\end{itemize}

>>>>

We use symbols $[K]=\{1,2,\dots,K\}$ for strong labels and $[\overline{K}]
=\{\overline{1},
\overline{2}, \dots, \overline{K}\}$ for weak labels. Formally, the weak
labeling problem can be described as below:
\begin{figure}[H]
\begin{framed}
\begin{center}
    \textbf{Weak Labeling}
\end{center}
\textbf{Given:} Feature-label pairs $(x_1, y_1)$, $(x_2, y_2)$, \dots, $(x_T, y_T)$ in $\{0,1\}^d \times \{1,2,\dots, K, \overline{1}, \overline{2}, \dots, \overline{K}\}$. \\
\textbf{Question:} Do there exist $ w_1, w_2, \dots, w_K \in \R^d$ such that for all $t=1,2,\dots,T$,
\begin{align*}
& y_t \in [K] \Longrightarrow \forall i \in [K] \setminus \{y_t\} \quad \ip{w_{y_t}}{x_t}  > \ip{w_i}{x_t} \; , \\
& \text{and} \\
& y_t \in [\overline{K}] \Longrightarrow \exists i \in [K] \quad \ip{w_i}{x_t} > \ip{w_{\overline{y_t}}}{x_t} \; ?
\end{align*}
\end{framed}
\end{figure}

@@

We create the weak labeling instance as follows. Let $d=N+1$ and $K=3$.
Define $\zero$ as the zero vector $(0,\dots,0)\in \R^N$ and $\e_i$ as the
$i$-th standard vector $(0,\dots, 1, \dots, 0)\in \R^N$. Then we include all
the following feature-label pairs:
\begin{itemize}
\item Type 1: $(x,y)=((\zero,1), 3)$,
\item Type 2: $(x,y)=((\e_i,1), \overline{3})$ for all $i \in \{1,2,\dots,N\}$,
\item Type 3: $(x,y)=\left(\left(\sum_{i\in c_j} \e_i, 1\right), 3\right)$ for all $j \in \{1,2,\dots,M\}$.
\end{itemize}

### 2019-05-08 ICML-camera-ready/title-and-abstract.tex
Fixes

\item Under the more challenging weak linear separability condition, we design
an efficient algorithm with a mistake bound of $\min (2^{\widetilde{O}(K \log^2
(1/\gamma))}, 2^{\widetilde{O}(\sqrt{1/\gamma} \log K)})$ \footnote{We use the notation
$\widetilde{O}(f(\cdot)) = O(f(\cdot) \polylog(f(\cdot)))$.}.
Our algorithm
is based on kernel Perceptron, which is inspired by the work
of \citet{Klivans-Servedio-2008} on improperly learning intersection of halfspaces.
%is based on a infinite-dimensional feature mapping that transforms weakly linear
%separable examples to strongly linear separable examples, which in turn is
%of \citet{Shalev-Shwartz-Shamir-Sridharan-2011},
\end{enumerate}
\end{abstract}

>>>>

\item Under the more challenging weak linear separability condition, we design
an efficient algorithm with a mistake bound of $\min (2^{\widetilde{O}(K \log^2
(1/\gamma))}, 2^{\widetilde{O}(\sqrt{1/\gamma} \log K)})$.\footnote{We use the
notation $\widetilde{O}(f(\cdot)) = O(f(\cdot) \polylog(f(\cdot)))$.} Our
algorithm is based on kernel Perceptron and is inspired by the work of
\citet{Klivans-Servedio-2008} on improperly learning intersection of halfspaces.
\end{enumerate}
\end{abstract}
